\documentclass[a4,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{mediumblue}{RGB}{0,102,204}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries\color{darkblue}
}{}{0em}{}[\color{mediumblue}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item[]
  \begin{minipage}[t]{\linewidth}
    \leavevmode\llap{\color{mediumblue}\scriptsize\textbullet\hspace{0.5em}}%
    \small{#1}\vspace{-1pt}
  \end{minipage}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.35in, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

% Resume subheading for Education (improved spacing)
\newcommand{\resumeSubheadingEdu}[4]{ % #1=Degree, #2=Period, #3=College, #4=Location
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darkblue}#1} & \textbf{\small\color{darkblue}#2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

% Work experience formatting: Position | Company, Location         Duration
\newcommand{\resumeSubheading}[4]{ % #1=Position, #2=Period, #3=Company, #4=Location
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darkblue}#1} \ \textbar \ \textit{\small #3, #4} & \textbf{\small\color{darkblue}#2} \\
    \end{tabular*}\vspace{-5pt}
}

% Project heading with better formatting
\newcommand{\resumeProjectHeading}[3]{ % #1=Project Name, #2=Technologies, #3=Date
    \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darkblue}#1} & \textbf{\small\color{darkblue}#3} \\
      \textit{\small #2} & \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% New command for skills with better formatting
\newcommand{\resumeSkillItem}[2]{
  \textbf{\color{darkblue}#1}{: #2}
}

\begin{document}

% HEADER SECTION - Improved with better spacing and color
\begin{center}
    {\Huge \scshape \color{darkblue}Richie Thomas} \\ 
    
    \vspace{6pt}
    \small 
    \raisebox{-0.1\height}{\color{mediumblue}\faPhone}\ +91-9920616539 \quad
    \href{mailto:richiebt2004@gmail.com}{\raisebox{-0.2\height}{\color{mediumblue}\faEnvelope}\ richiebt2004@gmail.com} \quad
    \href{https://linkedin.com/in/richie-thomas}{\raisebox{-0.2\height}{\color{mediumblue}\faLinkedin}\ linkedin.com/in/richie-thomas} \quad
    \href{https://github.com/richiebthomas}{\raisebox{-0.2\height}{\color{mediumblue}\faGithub}\ github.com/richiebthomas}
    \vspace{-6pt}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheadingEdu
      {Bachelor of Engineering - Information Technology}{2022 -- 2026}
      {Fr. C. Rodrigues Institute of Technology, Vashi}{CGPA: 7.42/10.0 (Sem 6)}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Research Intern}{July 2025 -- Present}
      {IISER}{Mohali}
      \resumeItemListStart
        \resumeItem{Architected a sparse neural network on a PYNQ-Z2 FPGA using Python and Vivado HLS, pruning near-zero weights to boost real-time edge AI performance while maintaining \textbf{96\% MNIST recognition accuracy}.}
        \resumeItem{Optimized matrix multiplication kernels with Vivado HLS pragmas (loop unrolling, pipelining), reducing latency by \textbf{3.2×} and improving throughput by \textbf{2.7×} compared to baseline FPGA implementation.}
      \resumeItemListEnd


\resumeSubheading
      {Full Stack Web Developer Intern}{March 2025 -- Sept 2025}
      {Bayside Sports}{Bandra}
      \resumeItemListStart
        \resumeItem{Built a Server-Side Rendered (SSR) sales portal using React.js and Laravel, cutting initial page load time by \textbf{50\%} and enhancing crawlability.}
        \resumeItem{Developed admin dashboard that cut lead qualification time by \textbf{40\%}, allowing sales reps to tailor outreach based on user booking data.}
      \resumeItemListEnd
\resumeSubheading
      {Backend Developer Intern}{July 2025 -- July 2025}
      {Sports Mentoring Infusion}{Mumbai}
      \resumeItemListStart
        \resumeItem{Architected a scalable educational management platform using Node.js, Express, and PostgreSQL, supporting multi-role authentication for \textbf{500+ students, coaches, and administrators} with JWT-based security.}
        \resumeItem{Developed comprehensive REST API with 12+ interconnected database tables, implementing gamified learning features including points system, badges, and real-time progress tracking, reducing manual administrative tasks by \textbf{60\%}.}
      \resumeItemListEnd


  \resumeSubheading
      {Android Developer Intern}{June 2025 -- July 2025}
      {GetFly Technologies}{Sion}
      \resumeItemListStart
        \resumeItem{Delivered a comprehensive campus ERP solution using Flutter for VPP College of Engineering, digitizing operations for over \textbf{1,000 students and faculty} across 8 modules.}
        \resumeItem{Established a unified, scalable project architecture by consolidating multiple codebases, integrating 8+ REST APIs, and optimizing data fetching to reduce sync latency by \textbf{40\%}.}
      \resumeItemListEnd

  \resumeSubheading
      {PHP Developer Intern}{March 2024 -- April 2025}
      {FCRIT}{Vashi}
      \resumeItemListStart
        \resumeItem{Enhanced and maintained a campus information management system by implementing new features based on faculty feedback and resolving critical bugs, improving usability for over \textbf{1,000 users}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
  \resumeSubHeadingListStart

  \resumeProjectHeading
      {ChatApp - End-to-End Encrypted Messenger}{Flutter, Node.js, E2E Encryption}{2025}
      \resumeItemListStart
        \resumeItem{Implemented hybrid encryption combining \textbf{Diffie-Hellman} key exchange (X25519) with \textbf{RSA}-style authentication (Ed25519) for secure session establishment, achieving military-grade encryption comparable to WhatsApp and Signal.}
        \resumeItem{Built Double Ratchet messaging with AES-GCM encryption, achieving perfect forward secrecy and post-compromise security.}
      \resumeItemListEnd

    \resumeProjectHeading
      {SMI - Behavior Management Platform}{React Native, Node.js, PostgreSQL}{2025}
      \resumeItemListStart
        \resumeItem{Built a comprehensive cross-platform educational management system using React Native (Expo) and Node.js, serving multiple user roles with real-time data synchronization.}
        \resumeItem{Designed and implemented PostgreSQL database with 12+ interconnected tables using UUID primary keys, integrated speech-to-text capabilities, and developed gamified learning features with points system and progress tracking analytics.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \resumeSkillItem{Languages}{JavaScript, Python, Java, Dart, SQL} \\[2pt]
     \resumeSkillItem{Frontend}{React.js, Flutter, React Native} \\[2pt]
     \resumeSkillItem{Backend}{Laravel, Node.js, Express, REST, GraphQL} \\[2pt]
     \resumeSkillItem{Databases}{PostgreSQL, MongoDB, Firestore, ORM (Prisma, Mongoose, Eloquent)} \\[2pt]
     \resumeSkillItem{DevOps}{Kubernetes, AWS, Docker, CI/CD, Git, Firebase, Postman} \\
    }}
 \end{itemize}

%-----------CO-CURRICULAR---------------
\section{CO-CURRICULAR AND VOLUNTARY ACTIVITIES}
  \resumeItemListStart
    \resumeItem{\textbf{Head of Documentation}, Computer Society of India: Oversaw documentation for \textbf{10+ technical events} with \textbf{500+ participants}; designed standardized templates and built an automated certification system using Python.}
    \resumeItem{\textbf{Finalist (Top 5)}, HackQuinox 2024 Hackathon, Computer Society of India – FCRIT.}
    \resumeItem{Advanced through the \textbf{Internal Round}, Smart India Hackathon 2024.}
    \resumeItem{\textbf{Organizing Committee Member}, ETAMAX 2024 (College Fest).}
    \resumeItem{\textbf{Top 20\%}, BuildWithIndia Hackathon by Google India.}
  \resumeItemListEnd

\end{document}
